\section{Moment maps}

\subsection{Hamiltonian and symplectic vector fields}

Let \((M, \omega)\) be a symplectic manifold.

\begin{definition}
    [Hamiltonian vector field] Let \(H : M \to \R\) be smooth. Then there exists a unique vector field \(X_H\) such that \(\iota_{X_H}\omega = \dd H\). \(X_H\) is called a Hamiltonian vector field, with Hamiltonian function \(H\).
\end{definition}

\begin{definition}
    [symplectic vector field]A vector field \(X\) on \(M\) preserving \(\omega\) is called symplectic, i.e. \(\mcL_X\omega = 0\).
\end{definition}

\begin{proposition}
    \(X\) is symplectic if and only if \(\iota_X\omega\) is closed, and \(X\) is Hamiltonian if and only if \(\iota_X\omega\) is exact.
\end{proposition}

Let \((M, \omega)\) be a symplectic manifold, \(G\) a Lie group, \(\psi : G \to \Diff(M)\) the smooth action of \(G\) on \(M\).

\begin{definition}
    [symplectic action] \(\psi\) is symplectic if \(\psi(g)\) is a symplectomorphism for all \(g \in G\).
\end{definition}

\subsection{Coadjoint representation}

Let \(G\) be a Lie group, with corresponding Lie algebra \(\mfg\).

\begin{definition}
    [coadjoint representation] The coadjoint representation of \(G\) is the representation \(\Ad^* : G \to \GL(\mfg^*)\) given by

    \[\Ad_g^*\xi(X) = \xi(\Ad_{g^{-1}}X)\]
\end{definition}

\subsection{Moment map}

Let \((M, \omega)\) be a symplectic manifold, \(G\) a Lie group, with Lie algebra \(\mfg\), and \(\psi : G \to \Sympl(M, \omega)\) a symplectic action.

\begin{definition}
    [Hamiltonian action] The action \(\psi\) is Hamiltonian if there exists a map \(\mu : M \to \mfg^*\) such that

    \begin{enumerate}
        \item For each \(X \in \mfg\), let
        {\begin{enumerate}[(i)]
            \item \(\mu^X : M \to \R\) be defined by \(\mu^X(p) = \mu(p)(X)\).
            \item \(X^\#\) the vector field on \(M\) generated by the one-parameter subgroup \(\exp(tX)\). That is,
            \[X^\#_p = \dv{t}\bigg\vert_{t =0}\bigg(\psi\left(\exp(t\xi)\right)(x)\bigg)\]

            Then

            \[\dd\mu^X = \iota_{X^\#}\omega\]

            i.e. \(\mu^X\) is a Hamiltonian function for the vector field \(X^\#\).
        \end{enumerate}}
        \item \(\mu\) is equivariant with respect to \(\psi\) and the coadjoint action \(\Ad^*\) of \(G\) on \(\mfg^*\), i.e.
        \[\mu \circ \psi_g = \Ad^*_g \circ \mu\]
    \end{enumerate}

    \((M, \omega, G, \mu)\) is called a Hamiltonian \(G\)-space, and \(\mu\) is called a moment map.
\end{definition}

\begin{definition}
    [comoment map]

    Suppose in addition \(G\) is connected. Then we can define a Hamiltonian action by a comoment map \(\mu^* : \mfg \to C^\infty(M)\), such that

    \begin{enumerate}
        \item \(\mu^*(X) = \mu^X\) is a Hamiltonian function for \(X^\#\),
        \item \(\mu^*\) is a Lie algebra homomorphism, i.e.
        \[\mu^*[X, Y] = \{\mu^*(X), \mu^*(Y)\}\]

        where \(\{\cdot, \cdot\}\) is the Poisson bracket on \(C^\infty(M)\).
    \end{enumerate}
\end{definition}

\subsection{Symplectic reduction}

\begin{theorem}
    [Marsden-Weinstein-Meyer] Let \((M, \omega, G, \mu)\) be a Hamiltonian \(G\)-space for a compact Lie group \(G\), \(i : \mu^{-1}(0) \to M\) be the inclusion map. Suppose \(G\) acts freely on \(\mu^{-1}(0)\). Then

    \begin{enumerate}
        \item the orbit space \(M_{\text{red}} = \mu^{-1}(0)/G\) is a smooth manifold,
        \item \(\pi : \mu^{-1}(0) \to M_{\text{red}}\) is a principal \(G\)-bundle,
        \item there is a symplectic form \(\omega_{\text{red}}\) on \(M_{\text{red}}\) such that \(\pi^*\omega_{\text{red}} = i^*\omega\),
    \end{enumerate}
\end{theorem}

\begin{definition}
    [Symplectic quotient] \((M_{\text{red}}, \omega_{\text{red}})\) is called the symplectic quotient of \((M, \omega)\) by \(G\).
\end{definition}

\subsection{Kirillov-Kostant}

Let \(G\) be a Lie group, with Lie algebra \(\mfg\).

For \(\xi \in \mfg^*\), define a skew-symmetric bilinear form on \(\mfg\) by

\[\omega_\xi(X, Y) = \xi([X, Y])\]

This defines a non-degenerate \(2\)-form on the tangent space at \(\xi\) of the coadjoint orbit through \(\xi\). Moreover, \(\omega_\xi\) is closed, and so we have a symplectic form the coadjoint orbits of \(\mfg^*\), called the Kirillov-Kostant form.
